### 2009-05-14 doc/tech_doc/jura/jura-tech-doc.tex
Documenting new features

@@

\section{Security}
The JURA executable runs with the same user priviliges as the A-REX,
typically as \textit{root}. The owner of a job log file is the local
user mapped for the submitter entity of the corresponding job. These
files contain confidential data, access to which must be restricted,
therefore read access is limited to the owner and the super user. If
JURA is executed by A-REX, it can read data from these files, and
delete expired files.

@@

The usage reporting part of the JURA code has a modular design in
order to enable adding other types of accounting services besides the
curently only supported LUTS. An abstract interface class called
``\textit{Destination}'' represents a usage reporting destination
service. Different inherited classes of ``\textit{Destination}''
handle different types of services. Currently the only inherited class
is ``\textit{LutsDestination}'', implementing support for LUTS. If one
wishes to develop a module for another service type, he or she has to
create a new descendant class of ``\textit{Destination}'', implement
its ``\textit{report()}'' method to submit the contents of the job log
file given as an argument, and adapt the static
``\textit{createDestination()}'' method of ``\textit{Destination}'' to
instantiate the appropriate class.

@@

The \textit{jobreport\_options} variable allows passing a generic
option string to JURA verbatim. This string can be used for example
for service-related settings. Currently only SGAS LUTS service is
supported, for which the UR batch size can be set with the following
configuration line:

\verb|jobreport_options="urbatch:size"|

where \textit{size} is a positive integer, the number of URs sent
within one request. If not given, the default is 50. Zero value means
unlimited batch size.

The example below is a part of the ``\textit{grid-manager}'' block of
the A-REX configuration. It enables logging of URs to two hosts, using
the host credential files (placed in the standard locations), with a
maximum of 50 URs per batch. Job log files expire after a week.
%EXAMPLE!
\begin{verbatim}
...
jobreport="https://luts1.nordugrid.org:8443/wsrf/services/sgas/LUTS"
jobreport="https://luts2.nordugrid.org:8443/wsrf/services/sgas/LUTS 7"
jobreport_credentials="/etc/grid-security/hostkey.pem /etc/grid-security/hostcert.pem 
     /etc/grid-security/certificates"
jobreport_options="urbatch:50"
...
\end{verbatim}

@@

\begin{itemize}
\item The time frequency of running JURA is not configurable. It is a
  hardcoded value in A-REX: 3600 seconds, i.e. one hour. 
\item The number of user-supplied reporting destinations is limited
  for the sake of robustness. This upper limit is hardcoded in A-REX:
  max. 3 destinations are parsed from JSDL, and max. 1 from RSL.
\item The \textit{arcsub} job submission client removes all but one
  reporting destination URL from the job description, further limiting
  the number of user-supplied destinations.
\item The current implementation of JURA and A-REX supports only one
  expiration time for all the reporting destinations. Even though the
  configuration enables the specification of different expiration
  values per reporting destination, it is not taken into account by
  the system, the last value is used as the common expiration time
  value.
\item It is not possible to use different credentials per destinations.
\item Some optional UR properties are not supported (see
  App.~\ref{log2ur}).
\item Memory is not reported correctly. A bug in GNU ``time'' results
  in all memory usage set incorrectly as zero.
\item Some necessary extensions to the generated UR are not yet filled
  though the information is already collected in the job log files.
\item Handling of runtime environment string is missing.
\item Detailed user identity information based on the X.509 proxy
  certificate content or other submitted credentials is missing from
  URs.
\end{itemize}

There is also plan to extend JURA with ther following features:

\begin{itemize}
\item An archiving functionality, storing generated URs in a local
  directory specified in the configuration.
\item Support for other accounting systems besides LUTS, especially
  the EGEE Accounting Service. However, appropriate documentation on
  the service interfaces is missing as of now.
\item Extend JURA to be able to read all necessary parameters
  (credentials, reporting targets) from the command line so that it
  can serve as a stand-alone reporting utility invoked independently
  from A-REX.
\item Enable generating coarser-grained ``\textit{Aggregate URs}''
  from multiple URs.
\item Investigate the subject of project-related charging: who is
  responsible for determining the ``\textit{charge}'' value; what rules should
  be applied?
\end{itemize}

@@

\begin{tabular}{|p{0.22\columnwidth}|p{0.22\columnwidth}|p{0.54\columnwidth}|}
\hline
\textbf{Generated\newline UR Property}&
\textbf{Source\newline(job log entry)}&
\textbf{Information content}\\
\hline\hline
RecordId&
nodename,\newline
ngjobid&
Globally unique identifier for UR\\
\hline
GlobalJobId&
globalid&
Globally unique identifier of job:\newline
XML element as defined by BES\\
\hline
LocalJobId&
localid&
CE-specific identifier of job\\
\hline
GlobalUserName&
usersn&
DN of submitting user's certificate\\
\hline
LocalUserId&
localuser&
POSIX user on CE executing the job\\
\hline
JobName&
jobname&
Name of job, as given in job description\\
\hline
Status&
status&
Status of job\\
\hline
WallDuration\newline $[$ISO 8601 duration$]$&
usedwalltime $[$s$]$&
Wall-clock time used by job\\
\hline
CpuDuration\newline $[$ISO 8601 duration$]$&
usedcputime $[$s$]$&
CPU time used by job\\
\hline
StartTime\newline $[$ISO 8601 time stamp$]$&
submissiontime\newline $[$ISO 8601 time stamp$]$&
Time instant the job started\\
\hline
EndTime\newline $[$ISO 8601 time stamp$]$&
endtime\newline $[$ISO 8601 time stamp$]$&
Time instant the job ended\\
\hline
MachineName&
nodename&
Name of the machine where the job ran\newline
(first node from colon-separated list put into element)\\
\hline
Host&
nodename&
System hostname(s) where the job ran\newline
(nodes from colon-separated list put into separate elements)\\
\hline
SubmitHost&
clienthost&
System hostname the job was submitted from\\
\hline
Queue&
lrms&
Name of the queue from which the job was executed\\
\hline
ProjectName&
projectname&
Name of project, as given in job description\\
\hline
Memory\newline
$[$average virtual, kB$]$&
usedmemory $[$kB$]$&
Average total memory used by job\\
\hline
Memory\newline
$[$max physical, kB$]$&
usedmaxresident $[$kB$]$&
Maximal resident memory used by job\\
\hline
Memory\newline
$[$average physical, kB$]$&
usedaverageresident $[$kB$]$&
Average resident memory used by job\\
\hline
NodeCount&
nodecount&
Number of nodes (physical machines) involved in the job.\\
\hline
ProcessID&
\textbf{MISSING}&
The process ID(s) of the job\\
\hline
Charge&
\textbf{MISSING}&
Total charge of the job (money or abstract credits)\\
\hline
Network&
\textbf{MISSING}&
Network usage of job\\
\hline
Disk&
\textbf{MISSING}&
Disk usage of job\\
\hline
Swap&
\textbf{MISSING}&
Swap usage of job\\
\hline
Processors&
\textbf{MISSING}&
Number of processors used or requested\\
\hline
TimeDuration&
\textbf{MISSING}&
Additionally measured time duration(s)\\
\hline
TimeInstant&
\textbf{MISSING}&
Additionally identified time instant(s)\\
\hline
ServiceLevel&
\textbf{MISSING}&
Quality of service associated with usage\\

%\hline
%\hline
%\textbf{Extra UR Property}&
%\textbf{Source\newline(job log entry)}&
%\textbf{Description}\\
%\hline\hline
%UserProxy&
%userproxy&
%Proxy of user, including VOMS info\\
%\hline
%RuntimeEnvironment&
%runtimeenvironment&
%Runtime environment info\\

>>>>

An archiving functionality allows to store generated URs in a
specified directory (see Section \ref{config}) on the disk. If
enabled, valid UR XMLs are written to files named
``\textit{usagerecord.$<$ngjobid$>$.$<$random$>$}'', where
``\textit{ngjobid}'' and ``\textit{random}'' match those of the source
job log file. If a job log file is processed repeatedly -- for example
because of temporary connection failures to a LUTS service -- and a
respective UR archive file already exists, then the UR is not
generated again. Instead, the contents of the archive file are used
without change (NB: the creation time stamp is also retained).

@@

\section{Security}
The JURA executable runs with the same user privileges as the A-REX,
typically as \textit{root}. The owner of a job log file is the local
user mapped for the submitter entity of the corresponding job. These
files contain confidential data, access to which must be restricted,
therefore read access is limited to the owner and the super user. If
JURA is executed by A-REX, it can read data from these files, and
delete expired files.

@@

The usage reporting part of the JURA code has a modular design in
order to enable adding other types of accounting services besides the
currently only supported LUTS. An abstract interface class called
``\textit{Destination}'' represents a usage reporting destination
service. Different inherited classes of ``\textit{Destination}''
handle different types of services. Currently the only inherited class
is ``\textit{LutsDestination}'', implementing support for LUTS. If one
wishes to develop a module for another service type, he or she has to
create a new descendant class of ``\textit{Destination}'', implement
its ``\textit{report()}'' method to submit the contents of the job log
file given as an argument, and adapt the static
``\textit{createDestination()}'' method of ``\textit{Destination}'' to
instantiate the appropriate class.

@@

The \textit{jobreport\_options} variable allows passing a generic
option string to JURA verbatim. This string is interpreted by JURA as
a comma-separated list of ``\textit{name:value}'' pairs (note the
colon!), which represent service-related settings and extended
reporting parameters. The job reporting options currently defined are:

\begin{itemize}
\item \textbf{\textit{urbatch}}\textit{:size} -- sets the maximal
  number of URs in the batch sent within one request. Zero value means
  unlimited batch size. Default is 50.
\item \textbf{\textit{archiving}}\textit{:dir} -- enables archiving of
  generated URs in the given directory. If the directory does not
  exist, an attempt is made to create it. If this option is absent, no
  archiving is performed.
\end{itemize}

The example below is a part of the ``\textit{grid-manager}'' block of
the A-REX configuration. It enables logging of URs to two hosts, using
the host credential files (placed in the standard locations), with a
maximum of 50 URs per batch. Generated URs are archived in the
directory ``\textit{/var/urs}''.
Job log files expire after a week.
%EXAMPLE!
\begin{verbatim}
...
jobreport="https://luts1.nordugrid.org:8443/wsrf/services/sgas/LUTS"
jobreport="https://luts2.nordugrid.org:8443/wsrf/services/sgas/LUTS 7"
jobreport_credentials="/etc/grid-security/hostkey.pem /etc/grid-security/hostcert.pem 
     /etc/grid-security/certificates"
jobreport_options="urbatch:50,archiving:/var/urs"
...
\end{verbatim}

@@

\begin{itemize}
\item The time frequency of running JURA is not configurable. It is a
  hardcoded value in A-REX: 3600 seconds, i.e. one hour. 
\item The number of user-supplied reporting destinations is limited
  for the sake of robustness. This upper limit is hardcoded in A-REX:
  max. 3 destinations are parsed from JSDL, and max. 1 from RSL.
\item The \textit{arcsub} job submission client removes all but one
  reporting destination URL from the job description, further limiting
  the number of user-supplied destinations.
\item The current implementation of JURA and A-REX supports only one
  expiration time for all the reporting destinations. Even though the
  configuration enables the specification of different expiration
  values per reporting destination, it is not taken into account by
  the system, the last value is used as the common expiration time
  value.
\item It is not possible to use different credentials per destinations.
\item Some optional UR properties are not supported (see
  App.~\ref{log2ur}).
\item Memory is not reported correctly. A bug in GNU ``time'' results
  in all memory usage set incorrectly as zero.
\item Some necessary extensions to the generated UR are not yet filled
  though the information is already collected in the job log files.
%\item Handling of runtime environment string is missing.
\item Detailed user identity information based on the X.509 proxy
  certificate content or other submitted credentials is missing from
  URs.
\end{itemize}

There is also plan to extend JURA with the following features:

\begin{itemize}
%\item An archiving functionality, storing generated URs in a local
%  directory specified in the configuration.
\item Support for other accounting systems besides LUTS, especially
  the EGEE Accounting Service. However, appropriate documentation on
  the service interfaces is missing as of now.
\item Extend JURA to be able to read all necessary parameters
  (credentials, reporting targets) from the command line so that it
  can serve as a stand-alone reporting utility invoked independently
  from A-REX.
\item Enable generating coarser-grained ``\textit{Aggregate URs}''
  from multiple URs.
\item Investigate the subject of project-related charging: who is
  responsible for determining the ``\textit{charge}'' value; what rules should
  be applied?
\end{itemize}

@@

\begin{tabular}{|p{0.21\columnwidth}|p{0.21\columnwidth}|p{0.56\columnwidth}|}
\hline
\textbf{Generated\newline UR Property}&
\textbf{Source\newline(job log entry)}&
\textbf{Information content}\\
\hline\hline
RecordId&
nodename,\newline
ngjobid&
Globally unique identifier for UR\\
\hline
GlobalJobId&
globalid&
Globally unique identifier of job:\newline
XML element as defined by BES\\
\hline
LocalJobId&
localid&
CE-specific identifier of job\\
\hline
GlobalUserName&
usersn&
DN of submitting user's certificate\\
\hline
LocalUserId&
localuser&
POSIX user on CE executing the job\\
\hline
JobName&
jobname&
Name of job, as given in job description\\
\hline
Status&
status&
Status of job\\
\hline
WallDuration\newline $[$ISO 8601 duration$]$&
usedwalltime $[$s$]$&
Wall-clock time used by job\\
\hline
CpuDuration\newline $[$ISO 8601 duration$]$&
usedcputime $[$s$]$&
CPU time used by job\\
\hline
StartTime\newline $[$ISO 8601 time stamp$]$&
submissiontime\newline $[$ISO 8601 time stamp$]$&
Time instant the job started\\
\hline
EndTime\newline $[$ISO 8601 time stamp$]$&
endtime\newline $[$ISO 8601 time stamp$]$&
Time instant the job ended\\
\hline
MachineName&
nodename&
Name of the machine where the job ran\newline
(first node from colon-separated list put into element)\\
\hline
Host&
nodename&
System hostname(s) where the job ran\newline
(nodes from colon-separated list put into separate elements)\\
\hline
SubmitHost&
clienthost&
System hostname the job was submitted from\\
\hline
Queue&
lrms&
Name of the queue from which the job was executed\\
\hline
ProjectName&
projectname&
Name of project, as given in job description\\
\hline
Memory\newline
$[$average virtual, kB$]$&
usedmemory $[$kB$]$&
Average total memory used by job\\
\hline
Memory\newline
$[$max physical, kB$]$&
usedmaxresident $[$kB$]$&
Maximal resident memory used by job\\
\hline
Memory\newline
$[$average physical, kB$]$&
usedaverageresident $[$kB$]$&
Average resident memory used by job\\
\hline
NodeCount&
nodecount&
Number of nodes (physical machines) involved in the job\\
\hline
ProcessID&
\textbf{MISSING}&
The process ID(s) of the job\\
\hline
Charge&
\textbf{MISSING}&
Total charge of the job (money or abstract credits)\\
\hline
Network&
\textbf{MISSING}&
Network usage of job\\
\hline
Disk&
\textbf{MISSING}&
Disk usage of job\\
\hline
Swap&
\textbf{MISSING}&
Swap usage of job\\
\hline
Processors&
\textbf{MISSING}&
Number of processors used or requested\\
\hline
TimeDuration&
\textbf{MISSING}&
Additionally measured time duration(s)\\
\hline
TimeInstant&
\textbf{MISSING}&
Additionally identified time instant(s)\\
\hline
ServiceLevel&
\textbf{MISSING}&
Quality of service associated with usage\\
\hline
\hline
\textbf{Extended\newline UR Property}&
\textbf{Source\newline(job log entry)}&
\textbf{Description}\\
\hline\hline
%UserProxy&
%userproxy&
%Proxy of user, including VOMS info\\
%\hline
RuntimeEnvironment&
runtimeenvironment&
Requested runtime environment, specified in job description\newline
(RTEs from space-separated list put into separate elements)\\
